paper1-wrangling

### 2023-10-12 paper1-INTERACT-data-prep.Rmd
Clean data prep code

Reformat column names to match the sd_all dataframe (format city_id to be all lowercase, rename datetime to date)
```{r}
  weather$city_id<-tolower(weather$city_id)
  weather<-weather %>% rename(date=date_time,
                              mean_temp=mean_temp_c,
                              max_temp=max_temp_c,
                              min_temp=min_temp_c,
                              total_precip=total_precip_mm)
```
Explore variables available
```{r}
  weather<-weather %>% dplyr::select(date,mean_temp,total_precip,city_id)
```

@@

# 2. person days where wearing == 1
  sd_wearing<-merge(sd_wearing,weather,by=c("date","city_id"),all.x=TRUE)

# 3. person days where wearing == 1 & in_city == 1
  sd_wearingCity<-merge(sd_wearingCity,weather,by=c("date","city_id"),all.x=TRUE)
  rm(weather)
```

@@

```{r}
  write.csv(sd_all,"sensdoc-all-2023.csv",row.names = FALSE)
  write.csv(sd_wearingCity,"sensdoc-wearingCity-2023.csv",row.names = FALSE)
  write.csv(sd_wearing,"sensdoc-wearing-2023.csv",row.names = FALSE)
```

>>>>

Reformat column names to match the sd_all dataframe (format city_id to be all lowercase, rename datetime to date)
```{r}
  weather$city_id<-tolower(weather$city_id)
  weather<-weather %>% rename(date=date_time,
                              mean_temp=mean_temp_c,
                              max_temp=max_temp_c,
                              min_temp=min_temp_c,
                              total_precip=total_precip_mm)
```

Explore variables available
```{r}
  weather<-weather %>% dplyr::select(date,mean_temp,total_precip,city_id)
```

@@

# 2. person days where wearing == 1
  sd_wearing<-merge(sd_wearing,weather,by=c("date","city_id"),all.x=TRUE)
```

@@

```{r}
  write.csv(sd_all,"Data//final-for-analysis//sensdoc-all-2023.csv",row.names = FALSE)
  write.csv(sd_wearing,"Data//final-for-analysis//sensdoc-wearing-2023.csv",row.names = FALSE)
```
